Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-05-31 cordillera-cycle.tex
Begin to work on the discussion.

The modelled last glacial maximum ice sheet possess a central divide located at
about 3\,500\,\unit{m} elevation along the spine of the Rocky Mountains. The
distribution of surface velocites shows a clear assymetry between the maritime,
western flank, and the continental, eastern flank of the ice sheet
(Fig.~\ref{fig:lgm}).

@@

\note{At this stage, this section is just a collection of thoughts that need to
be developed into paragraphs. Please comment, criticize, add your own ideas.}

\subsection{Timing of glaciation}

Timing of glaciation is better reproduced by Greenland and Antarctic records than
nearby oceanic records. This is because the oceanic cores are affected by
variations in strength of a local current (the California current) associated
with the presence of the ice sheet. The timing of the LGM is better reproduced
by Antarctic than Greenland records.

\subsection{Extent of glaciation}

>>>>

The modelled last glacial maximum ice sheet possess a central divide located at
about 3\,500\,\unit{m} elevation along the spine of the Rocky Mountains. The
distribution of surface velocities shows a clear asymmetry between the
maritime, western flank, and the continental, eastern flank of the ice sheet
(Fig.~\ref{fig:lgm}).

@@

\subsection{Ice-sheet scale glaciation dynamics}

During the last glacial cycle, geomorphological evidence has allowed to
identify two major advances of the Cordilleran ice sheet. These correspond to
the last glacial maximum \aref, and the older xxx glaciation, found in the
northernmost parts of the ice sheet \aref. It should be noted that all
simulations presented here reproduce these two major events, which constitutes
a first-order agreement between model results and geomorphological evidence.

However, the timing of these events depends highly on the choice of temperature
time-series used to force the model. For instance, the timing of the last
glacial maximum is best reproduced by the Antarctic records, while simulations
driven by the NGRIP and oceanic records pre-date the last glacial maximum by
several thousands of years. Regarding the oceanic records, the early volume
maxima can be explain by an early warming in the palaeo-temperature record.
This early warming has been previously documented, and explained as a
weakening of the California current, precisely associated with the presence of
the Cordilleran ice sheet \aref. This precocious glacial maximum illustrates
the complexity of climate-ice-sheet feedbacks on a regional scale, and shows
that, although closely located to the modelling domain, the ODP~1012 and
ODP~1020 proxy records records can't be reliably used as a temperature forcing
to model the last Cordilleran ice sheet.
